Competing Bandits: The Perils of Exploration under Competition

### 2018-09-06 paper/content/introduction.tex
Added a para on mean reputation.

>>>>

\asedit{We also investigate how algorithms' performance ``in isolation" (without competition) is predictive of the outcomes under competition. In particular, we find that mean reputation -- arguably, the most natural performance measure ``in isolation" -- is sometimes not a good predictor. We suggest a more refined performance measure, and use it to explain (and frame) some of the competition outcomes.}
